---
title: My first notebook
author:  Alexia Cardona
date: 1 October 2019
output:
  html_document:
    toc: true
    toc_float:
      collapsed: true
---

# Heading 1 {#head1}

text after heading

**Bold bold** text here  
*italic* text here

^superscript^ text here

~subscript~ text here

`code` text here

~~strikethrough~~ text

## Header 2

[text of link](http://rpubs.com/JMcMurry/534236)


### Header 3

asdhaslkjdhaskldalsdkasd
aasdasdasd


asdasd
asd

asd

#### Header 4

You can find more information in [this section](#head1)

Bla bla bla [^1]

[^1]: This is footer number 1.

## Lists
1. Item 1
    a. Sub item 1.a  
    b. Sub item 1.b
2. Item 2
3. Item 3
<!-- do not show this on the report -->


* Item 1
* Item 2
* Item 3


# Images

<img src="img/Rlogo.svg" width=200 />

![This is the figure caption](img/Rlogo.svg)

# Tables

| Column 1 | Column 2|
|----------|---------|
| Item 1   | Item 2  |
| Item 2   | Item 3 |

# Blocks

```
print("Hello world")
x <- 1 + 2
```

# Inserting R code chunks

```{r message=FALSE}
library(tidyverse)

pop_data <- read_csv("data/gapminder_data.csv")

#create a table with only European countries in 2007 showing countries with largest life expactancy first
euro_data_tbl <- pop_data %>% 
                    filter(continent == "Europe" & year == 2007) %>% 
                    arrange(desc(lifeExp)) %>% 
                    select(-continent, -year)
```

The top countries in Europe that has the largest life expectancy in 2007 as shown in the table below:

```{r echo=FALSE}
library(rmarkdown)
paged_table(euro_data_tbl)
```


```{r}
#create a dataset that will be used to plot an image
euro_data_fig <- pop_data %>% 
                    filter(continent=="Europe") %>% 
                    mutate(year=as.factor(year))
```

```{r fig.cap="Life expactancy in Europe"}
euro_data_fig %>% 
                ggplot(mapping=aes(x=year, y=lifeExp)) +
                geom_violin()
```







